---
title: "Cohort Lexicase Data Analyses"
output: 
  html_document: 
    keep_md: yes
    toc: true
    toc_float: true
    toc_depth: 4
    collapsed: false
    theme: default
  pdf_document:
    toc: true
    toc_depth: 4
---

## Overview

Here, an overview of what we do in this here document.

## Analysis Setup

First, we'll load our R packages.

```{r, message=FALSE}
library(tidyr)      # (Wickham & Henry, 2018)
library(ggplot2)    # (Wickham, 2009)
library(plyr)       # (Wickham, 2011)
library(dplyr)      # (Wickham et al., 2018)
library(cowplot)    # (Wilke, 2018)
library(readr)
library(rcompanion) # (Mangiafico, 2019)
library(multcompView)

```

## Data Loading

Note, the path information used here is accurate for the directory structure used in our Git repository (LINK ANONYMIZED).

First, we'll load solution data after a fixed number of _evaluations_:

```{r}
# (1) After 26214400 total evaluations (100 generations of std lex)
solutions_e26214400_data_loc <- "../data/exp-data/min_programs__eval_26214400.csv"
prog_solutions_e26214400 <- read.csv(solutions_e26214400_data_loc, na.strings = "NONE")

# (2) After 78643200 total evaluations (300 generations of std lex)
solutions_e78643200_data_loc <- "../data/exp-data/min_programs__eval_78643200.csv"
prog_solutions_e78643200 <- read.csv(solutions_e78643200_data_loc, na.strings = "NONE")

# (3) Load summary of solution data (contingency tables), which contains both time points.
prog_solutions_evals_summary <- read.csv("../data/exp-data/min_programs__eval_all__solutions_summary.csv", na.strings = "NONE")
```

Below, we impose an ordering on the problems in the data (to make order of appearance in plotting consistent).

```{r}
prog_solutions_evals_summary$problem <- factor(prog_solutions_evals_summary$problem, levels=c('small-or-large','for-loop-index','compare-string-lengths','median','smallest'))

prog_solutions_e78643200$problem <- factor(prog_solutions_e78643200$problem, levels=c('small-or-large','for-loop-index','compare-string-lengths','median','smallest'))

# A map from data column name to name to be used in figures.
problem_names <- c(
  'small-or-large'=        "Small or Large",
  'for-loop-index'=        "For Loop Index",
  'compare-string-lengths'="Comp. Str. Lengths",
  'median'=                "Median",
  'smallest'=              "Smallest"
)
```

## Given a Fixed number of evaluations (26214400), both cohorts and downsampling improve problem solving success

## Down sampling

```{r, echo=FALSE}
# paper_plot_data <- filter(prog_solutions_evals_summary, test_mode=="SEL_COHORT_LEX" & ((problem=="small-or-large"&evaluation=="78643200")|(problem!="small-or-large"&evaluation=="26214400")))
downsample_data <- filter(prog_solutions_evals_summary, (test_mode=="SEL_DOWN_SAMPLE_TESTS"|cohort_config=="cn1:cs512") & evaluation=="26214400")

prob_data <- filter(downsample_data, problem=="compare-string-lengths")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- letters

prob_data <- filter(downsample_data, problem=="for-loop-index")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)

prob_data <- filter(downsample_data, problem=="median")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)

prob_data <- filter(downsample_data, problem=="small-or-large")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)

prob_data <- filter(downsample_data, problem=="smallest")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)

ggplot(data = downsample_data, mapping=aes(x=cohort_config, y=solutions_found, fill=cohort_config)) +
      geom_bar(stat="identity") + xlab("K (number of cohorts)") + ylab("Successful Runs")  +  ylim(0, 50) +
      scale_x_discrete(labels = c("1", "2", "4", "8", "16", "32", "64", "128", "256"), limits = c("cn1:cs512", "cn2:cs256", "cn4:cs128", "cn8:cs64", "cn16:cs32", "cn32:cs16", "cn64:cs8", "cn128:cs4", "cn256:cs2")) +
      guides(fill=FALSE)+
      geom_text(aes(label=solutions_found), nudge_y=2) + 
      theme(axis.title.x = element_text(size=14)) + 
      coord_flip() + facet_wrap( ~ problem, labeller=as_labeller(problem_names), nrow=1) + 
      theme(strip.text.x = element_text(size = 14)) + 
      ggtitle("Success Rates for Each Down-sample Configuration") +
      geom_text(aes(label=lab), data=all_letters, nudge_y = 8)

```

#### Statistics - Compare string lengths

```{r}
prob_data <- filter(downsample_data, problem=="compare-string-lengths")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - For loop index

```{r}
prob_data <- filter(downsample_data, problem=="for-loop-index")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - Median

```{r}
prob_data <- filter(downsample_data, problem=="median")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - Small or large

```{r}
prob_data <- filter(downsample_data, problem=="small-or-large")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - Smallest

```{r}
prob_data <- filter(downsample_data, problem=="smallest")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```


## Cohorts

```{r, echo=FALSE}
# paper_plot_data <- filter(prog_solutions_evals_summary, test_mode=="SEL_COHORT_LEX" & ((problem=="small-or-large"&evaluation=="78643200")|(problem!="small-or-large"&evaluation=="26214400")))
cohort_data <- filter(prog_solutions_evals_summary, test_mode=="SEL_COHORT_LEX" & evaluation=="26214400")

prob_data <- filter(cohort_data, problem=="compare-string-lengths")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- letters

prob_data <- filter(cohort_data, problem=="for-loop-index")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)

prob_data <- filter(cohort_data, problem=="median")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)

prob_data <- filter(cohort_data, problem=="small-or-large")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)

prob_data <- filter(cohort_data, problem=="smallest")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
mat <- pairwiseNominalMatrix(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
l <- multcompLetters(mat$Adjusted)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, prob_data)

all_letters <- rbind(all_letters, letters)



ggplot(data = cohort_data, mapping=aes(x=cohort_config, y=solutions_found, fill=cohort_config)) +
      geom_bar(stat="identity") + xlab("K (number of cohorts)") + ylab("Successful Runs")  +  ylim(0, 50) +
      scale_x_discrete(labels = c("1", "2", "4", "8", "16", "32", "64", "128", "256"), limits = c("cn1:cs512", "cn2:cs256", "cn4:cs128", "cn8:cs64", "cn16:cs32", "cn32:cs16", "cn64:cs8", "cn128:cs4", "cn256:cs2")) +
      guides(fill=FALSE)+
      geom_text(aes(label=solutions_found), nudge_y=2) + 
      theme(axis.title.x = element_text(size=14)) + 
      coord_flip() + facet_wrap( ~ problem, labeller=as_labeller(problem_names), nrow=1) + 
      theme(strip.text.x = element_text(size = 14)) + 
      ggtitle("Success Rates for Each Down-sample Configuration") +
      geom_text(aes(label=lab), data=all_letters, nudge_y = 8)

```


#### Statistics - Compare string lengths

```{r}
prob_data <- filter(cohort_data, problem=="compare-string-lengths")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - For loop index

```{r}
prob_data <- filter(cohort_data, problem=="for-loop-index")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - Median

```{r}
prob_data <- filter(cohort_data, problem=="median")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - Small or large

```{r}
prob_data <- filter(cohort_data, problem=="small-or-large")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```

#### Statistics - Smallest

```{r}
prob_data <- filter(cohort_data, problem=="smallest")
prob_data$successful_runs = prob_data$solutions_found
prob_data$failed_runs = prob_data$total_runs - prob_data$solutions_found
con_table <- matrix(c(prob_data$successful_runs, prob_data$failed_runs), nrow=length(prob_data$successful_runs))
rownames(con_table) <- prob_data$cohort_config
colnames(con_table) <- c("Successful Runs", "Failed Runs")
pairwiseNominalIndependence(con_table, fisher=TRUE, gtest=FALSE, chisq=FALSE, method="holm")
```












## Down sampling and cohort lexicase solves problems with less computational effort

## Down sampling

```{r, echo=FALSE}
downsample_ce_data <- filter(prog_solutions_e78643200, (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & problem!="small-or-large")

#eval_data <- filter(prog_solutions_e78643200, problem=="small-or-large" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
#kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
#p <- pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")
#l <- multcompLetters(p$p.value)
#letters <- data.frame(lab=l$Letters)
#letters$cohort_config <- rownames(letters)
#letters$lab <- sprintf("(%s)",letters$lab)
#letters <- merge(letters, eval_data)

#all_letters <- letters

eval_data <- filter(prog_solutions_e78643200, problem=="for-loop-index" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
p <- pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")
l <- multcompLetters(p$p.value)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, eval_data)

all_letters <- letters

eval_data <- filter(prog_solutions_e78643200, problem=="compare-string-lengths" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
p <- pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")
l <- multcompLetters(p$p.value)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, eval_data)

all_letters <- rbind(all_letters, letters)

eval_data <- filter(prog_solutions_e78643200, problem=="median" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
p <- pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")
l <- multcompLetters(p$p.value)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, eval_data)

all_letters <- rbind(all_letters, letters)

eval_data <- filter(prog_solutions_e78643200, problem=="smallest" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
p <- pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")
l <- multcompLetters(p$p.value)
letters <- data.frame(lab=l$Letters)
letters$cohort_config <- rownames(letters)
letters$lab <- sprintf("(%s)",letters$lab)
letters <- merge(letters, eval_data)

all_letters <- rbind(all_letters, letters)

ggplot(downsample_ce_data, mapping=aes(x=cohort_config, y=evaluation_first_solution_found, fill=cohort_config, colour=cohort_config)) +
    # geom_point(position = position_jitter(width = .15), size = .25) +
    geom_boxplot(aes(x = cohort_config, y = evaluation_first_solution_found), alpha = 0.3) +
    ylab("Test Case Evaluations") + ylim(0, 78643200) + xlab("K (number of cohorts)") +  guides(fill=FALSE, colour=FALSE) +
    scale_x_discrete(labels = c("1", "2", "4", "8", "16", "32", "64", "128", "256"), limits = c("cn1:cs512", "cn2:cs256", "cn4:cs128", "cn8:cs64", "cn16:cs32", "cn32:cs16", "cn64:cs8", "cn128:cs4", "cn256:cs2")) +
    ggtitle("Number of evaluations before finding a solution with down-sample") + 
    facet_wrap( ~ problem, labeller=as_labeller(problem_names), nrow=1) +
    theme(axis.title.x = element_text(size=14)) + 
    theme(strip.text.x = element_text(size = 12)) +
    geom_text(aes(label=lab), data=all_letters, nudge_x = 8)
```

#### Statistics - Small Or Large

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="small-or-large" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

#### Statistics - For Loop Index

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="for-loop-index" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

#### Statistics - Compare String Lengths

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="compare-string-lengths" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

#### Statistics - Median

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="median" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```


#### Statistics - Smallest

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="smallest" & (sel_mode == "sample tests"|cohort_config=="cn1:cs512") & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

## Cohorts

```{r, echo=FALSE}
cohort_ce_data <- filter(prog_solutions_e78643200, sel_mode == "cohort lex" & problem!="small-or-large")

ggplot(cohort_ce_data, mapping=aes(x=cohort_config, y=evaluation_first_solution_found, fill=cohort_config, colour=cohort_config)) +
    # geom_point(position = position_jitter(width = .15), size = .25) +
    geom_boxplot(aes(x = cohort_config, y = evaluation_first_solution_found), alpha = 0.3) +
    ylab("Test Case Evaluations") + ylim(0, 78643200) + xlab("K (number of cohorts)") +  guides(fill=FALSE, colour=FALSE) +
    scale_x_discrete(labels = c("1", "2", "4", "8", "16", "32", "64", "128", "256"), limits = c("cn1:cs512", "cn2:cs256", "cn4:cs128", "cn8:cs64", "cn16:cs32", "cn32:cs16", "cn64:cs8", "cn128:cs4", "cn256:cs2")) +
    ggtitle("Number of evaluations before finding a solution with cohort lexicase") + 
    facet_wrap( ~ problem, labeller=as_labeller(problem_names), nrow=1) +
    theme(axis.title.x = element_text(size=14)) + 
    theme(strip.text.x = element_text(size = 12))
```

#### Statistics - Small Or Large

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="small-or-large" & sel_mode == "cohort lex" & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

#### Statistics - For Loop Index

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="for-loop-index" & sel_mode == "cohort lex" & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

#### Statistics - Compare String Lengths

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="compare-string-lengths" & sel_mode == "cohort lex" & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

#### Statistics - Median

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="median" & sel_mode == "cohort lex" & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```


#### Statistics - Smallest

```{r}
eval_data <- filter(prog_solutions_e78643200, problem=="smallest" & sel_mode == "cohort lex" & !is.na(evaluation_first_solution_found))
kruskal.test(evaluation_first_solution_found ~ cohort_config, eval_data)
pairwise.wilcox.test(x=eval_data$evaluation_first_solution_found, g=eval_data$cohort_config, exact=FALSE, p.adjust.method = "holm")

cfgs <- c()
meds <- c()
for (cfg in levels(eval_data$cohort_config)) {
  cfgs <- c(cfgs, cfg)
  med  <- median(filter(eval_data, cohort_config==cfg)$evaluation_first_solution_found)
  meds <- c(meds, med)
}
df<-as.data.frame(x=cfgs)
df$medians<-meds
arrange(df, meds)
```

## References

Claus O. Wilke (2018). cowplot: Streamlined Plot Theme and Plot Annotations for 'ggplot2'. R package version 0.9.3.
  https://CRAN.R-project.org/package=cowplot

Helmuth, T., & Spector, L. (2015). General Program Synthesis Benchmark Suite. In Proceedings of the 2015 on Genetic and Evolutionary Computation Conference - GECCO ’15 (pp. 1039–1046). New York, New York, USA: ACM Press. https://doi.org/10.1145/2739480.2754769

R Core Team (2016). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL
  https://www.R-project.org/.

H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2009.

Hadley Wickham and Lionel Henry (2018). tidyr: Easily Tidy Data with 'spread()' and 'gather()'
Functions. R package version 0.8.1. https://CRAN.R-project.org/package=tidyr

Hadley Wickham (2011). The Split-Apply-Combine Strategy for Data Analysis. Journal of Statistical
Software, 40(1), 1-29. URL http://www.jstatsoft.org/v40/i01/.

Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2018). dplyr: A Grammar of Data
Manipulation. R package version 0.7.5. https://CRAN.R-project.org/package=dplyr

Salvatore Mangiafico (2019). rcompanion: Functions to Support Extension Education Program Evaluation. R package
  version 2.0.10. https://CRAN.R-project.org/package=rcompanion